\documentclass[12pt,a5paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\author{Kochenyuk Anatoly}
\title{summary 1 -- 6}
\begin{document}

\maketitle
The Time Traveller tell people, situated around about 4th dimension. They didn't believed him and then The Time Traveller show his prototype of the Time Mashine. And it was gone.

The next week all the group find The Time Traveller looking very tired. After dinner, he began to tell his story.

1st of all he travelled for 5 hours through the time.

Then he started his big time travel, by pushing the start lever.

Throughout the travel he saw days and nights changing each other, trees  becomng green, brown and green again.

Then he stop the machine, because of very big fear.

There was a heavy rain in the time that he travelled to.

After that he saw enourmous figures through the rain. He went back to the machine and he was ready to go back to the past.

Then he saw a couple of man going to go to him. They were very beautiful but thin. Noticing that his confidence returned and he took his hands from the machine. 

Also author spent full chapter to tell us about future people living? and looking.

Big mouthes and ears were changed to small ones, because of sound pollution was gone.

Difference between men and women also had disappeared. There was no any need of strong men protecting families from others. It was what author thinked about, but it's not completely true indeed.

Time Traveller with some sign tell them, that he became from the sun, by thunder.

Then he was shown to other people.

Future people eat only fruits.

Then he leave him alone 

Also people of future was very similar at clothes. Shops, advertisment, bying and selling was gone too.

Time Traveller said, that our farming is only in early stage.

Suddemnly he realised, that his Time Machine was gone from lawn, he trave to.

Crying, she was runnning there and then layed on the ground and fell asleep.

When he woke up, he desided to Either find his machine or build another one.

Then he got out of patience.

And then he thinked about situation, he is in, and laughed at himself.

\end{document}
